---
title: POST IN PROGRESS-Golf, Tidy Data, and Using Data Analysis for Strategy
author: ''
date: '2018-05-27'
publishdate: "2018-06-01"
slug: golf-tidy-data-and-using-data-analysis-for-strategy
draft: true
categories:
  - R
tags:
  - r
  - data-science
  - tidy-data
  - web-scraping
  - golf
  - strategy
  - data-analysis
subtitle: ''
output: 
  html_document: 
    toc: yes
    toc_depth: 4
    code_folding: hide
---

## Introduction

I'm going to use this post to discuss some of the aspects of data science that interest me most (using data to guide strategy and tidy data). First, I'm going to look at acquiring data from a webpage. In my opinion, this data isn't in a tidy format, and needs to be reshaped a bit. Once we get the data into a tidy form, we can 

## Getting the data

```{r message = FALSE, warning = FALSE}
library(tidyverse)
library(rvest)
library(scales)
theme_set(theme_bw())
```

I wrote the `full_scrape` function to pull in the data.

```{r}
full_scrape <- function(url){
  
  #read webpage and return tables
  all_tbls <- read_html(url) %>%
    html_nodes('table')
  # only select tables with scores
  all_tbls <- all_tbls[grepl(pattern = 'border="1"',
                             x = all_tbls)]
  # extract tables
  tbl_list <- lapply(all_tbls,
                     html_table,
                     header = TRUE)
  # convert column names to upper case
  tbl_list <- lapply(tbl_list, 
                     FUN = function(x) setNames(x, toupper(names(x))))
  # extract common names
  common_names <- Reduce(intersect, lapply(tbl_list, names))
  # bind tables together
  final_tbl <- do.call('rbind', 
                       lapply(tbl_list, FUN = function(x) x[common_names]))
  
  final_tbl
}
```


```{r cache = TRUE}
course_links <- 
  c("https://www.wiaawi.org/Portals/0/PDF/Results/Golf_Boys/2011/maarathonsectional.htm",
    "https://www.wiaawi.org/Portals/0/PDF/Results/Golf_Boys/2012/marathonsectional.htm",
    "http://www.golfcoacheswi.org/EventScoring/WIAA/boysgolf2013venuescores.php?course=Marathon",
    "http://www.wiaawisc.org/Golf/boys2014venuescores.php?course=Marathon+HS",
    "http://www.wiaawisc.org/Golf/boysgolf2015venuescores.php?course=Marathon+High+School",
    "http://www.wiaawisc.org/Golf/boysgolf2016venuescores.php?course=Marathon+HS",
    "http://www.wiaagolf.org/ScoreEntry/boysgolf2017venuescores.php?course=Marathon+HS")

tourn_type = c('sectionals', 
               'sectionals', 'regionals', 'regionals', 
               'sectionals','sectionals', 'regionals')

tourn_year <- 2011:2017

course_tables <- lapply(course_links, full_scrape)

course_tables <- lapply(1:length(course_tables), FUN = function(i){
    course_tables[[i]] %>%
        mutate(tourn_type = tourn_type[i],
               tourn_year = tourn_year[i])
})

common_names <- Reduce(intersect, lapply(course_tables, names))

course_tables <- do.call('rbind',
                         lapply(course_tables, 
                                FUN = function(x) x[common_names]))

# clean up results

course_tables <- course_tables[!is.na(course_tables$`1`),] %>%
  filter(TOT != 'DQ') %>% 
  mutate(NAME = paste0('A', row_number())) # ids


```


```{r}
# course data
pv_course <- data_frame(hole = as.character(1:18),
                        par = c(5, rep(4, 4), 3, rep(4, 2), 3,
                                4, 5, 4, 3, 5, rep(4,2), 3, 4),
                        OB = c(T, F, T, T, F, F, F, T, T,
                               T, F, T, F, F, F, F, F, T),
                        water = c(rep(T, 5), F, T, T, T,
                                  T, F, F, T, F, T, T, T, T),
                        side = rep(c('front', 'back'), each = 9))

tidy_scores <- course_tables %>%
  gather(hole, score, 
         -NAME, -YEAR, -OUT, -IN, -TOT,
         -tourn_type, -tourn_year) %>%
  mutate(score = as.numeric(score)) %>%
  inner_join(pv_course) %>%
  mutate(rel_to_par = score - par)
```

```{r}
simple_model <- lm(rel_to_par ~ 
                     as.factor(YEAR) + side + as.factor(par) + 
                     OB + water, data = tidy_scores)
```

